\documentclass[11pt,letter,sans]{moderncv}
\moderncvstyle{classic}
\nopagenumbers{}
\usepackage[margin=0.80in, scale=0.8]{geometry}
\setlength{\hintscolumnwidth}{3cm}


\firstname{Parth}
\familyname{Upadhyay}
\address{2704 Salado St. \#204}{Austin, TX 78705}
\mobile{832-286-8664}
\email{parth.upadhyay@gmail.com}

\begin{document}
\maketitle

\section{Education}
\cventry
{08/10 - 05/15}
{University of Texas at Austin}
{B.S. in Computer Science, \textbf{GPA: 3.84 / 4.00}}
{}
{}
{\textbf{Honors Programs: Dean's Scholars, Turing Scholars}}
\cvitem{Relevant Coursework:}
%{ Data Structures and Algorithms, Computer
  %Systems I/II, Advanced Operating Systems, Programming Languages, Graduate
%Compilers, Artificial Intelligence, Logic I/II}
{Advanced Operating Systems, Graduate Compilers, Artificial Intelligence,
Programming Languages, Computer Networks, Multicore Programming, Automata Theory}

\section{Employment History}
\cventry
{05/13 - 08/13}
{Software Development Intern}
{Square}
{San Francisco, CA}
{}
{Worked on a full-stack team developing various Square services with extensive
TDD. Primarily wrote backend ruby, but also spent time working in Javascript.
}

\cventry
{01/13 - 05/13}
{Teaching Assistant, Operating Systems}
{Dr. Michael Walfish}
{}
{}
{Assisted students with subject matter by leading discussion sections, office hours.}

\cventry
{05/12 - 08/12}
{Software Development Intern}
{Facebook}
{Seattle, WA}
{}
{Worked on the Real Time Infrastructure Team, specifically with Chat.
  \begin{itemize}
    \item Built and improved upon tools for assessing chat reliability
\end{itemize}}

\cventry
{11/11 - 05/12}
{Software Development Intern}
{Loku}
{Austin, TX}
{}
{Startup trying to solve the problem of local search. Assisted in the
development of a distributed webcrawler framework using Node.js and redis.}

\cventry
{08/11 - 12/11}
{Undergraduate Teaching Assistant - Research Methods}
{University of Texas}
{}
{}
{A unique class taught by the Dean and offered to Dean's Scholars and other
  Honors Students as a precursor to the Freshmen Research Initiative.
  \begin{itemize}
    \item Mentored a small group of students in the area of research and
      independent inquiry.
\end{itemize}}

\cventry
{05/11 - 08/11}
{Financial Software Development Intern}
{Bloomberg L.P.}
{New York, NY}
{}
{
  \begin{itemize}
    \item Built infrastructure to support data retrieval from new exchanges
    \item Developed internal tools to optimize quality control in the
      development process
\end{itemize}}

% \section{Research}
% \cventry
% {08/11 - 12/11}
% {Client Driven Pointer Analysis}
% {Advisor: Calvin Lin}
% {}
% {}
% {Implemented a subset of Samuel Guyer's Ph.D Thesis concerning "client driven
% pointer analysis" in LLVM with a team of undergraduates.}

% \cventry
% {01/11 - 05-11}
% {Freshmen Research Initiative: Autonomous Vehicles}
% {Advisor: Michael Quinlan}
% {}
% {}
% {Worked on developing infrastructure to help the autonomous vehicle react more
% dynamically to signs.}

\section{Skills}
\cvitem{Proficient}
{Java, Ruby, C/C++, *NIX platforms}
\cvitem{Experienced}
{Python, Javascript, Node.js, JQuery, HTML/CSS, Git, rspec}

%\cvitem{Projects}
%{Implemented a threadpool and network proxy in C; Implementing large parts of
  %the JOS operating system; On a team that won "Best Mobile App" at the UT
  %Yahoo Hackathon; Participated in 3 Day Startup building a social media
%aggregation service for small businesses.}

\section{Organizations}
\cvitem{Texas 4000 2014 - Equipment Coordinator}
{Member of the nonprofit organization Texas 4000 where each member raises
\$4,500 for cancer research in addition to biking 4000 miles from Austin to
Alaska to raise awareness and engage local communities. Responsible for all
gear and equipment issues on my route before and during the 4,500 ride. }

%\cvitem{Dean's Scholars Council}
%{Led high school tutoring, community service events, and organized social events
%to engage dean's scholars with the community and one another.}

\end{document}
